Autocorrelation in Sparse Distributed Memory

### 2019-09-23 paperIEEE.tex
init-paper-softwareX

Our conclusion is that this work is of special relevance as it brings about some \emph{systemwide properties} that models need to take into account.  The first decision choice involved in building a system with SDM regards the size of $n$, the number of dimensions of the memory.  Here, complementing the work of \cite{sjodin_improving_1995, sjodin_convergence_1998} in Jaeckel's SDM design\cite{jaeckel1989class}, we show that as $n$ grows, autocorrelation tends to $0$.  But recall that as $n$ grows, the size of the critical distance also tends to $0$.  It is therefore crucial to select a value for $n$ in which the model will retain its convergence properties, with the understanding of the possible effects brought about by autocorrelation.   Systemwide properties such as these affect the entire behavior of the model and, as such, should always be taken into account by theoreticians and modelers alike.

@@

  \caption{Bongard problems 71 - 74, courtesy of Dr. Harry Foundalis\cite{foundalis_phaeaco:_2006, douglas1980godel, bongard_recognition_1968, Linhares2000}.  What distinguishes the boxes on the left hand side to those on the right hand side?  This is the quintessential `system-2' type of problem that current lies beyond AI's capabilities. The reader should note that here, for each class, $n=6$, a hard task for Machine Learning.}

@@

>>>>

Our conclusion is that this work is of special relevance as it brings about some \emph{systemwide properties} that models need to take into account.  The first decision choice involved in building a system with SDM regards the size of $n$, the number of dimensions of the memory.  Here, complementing the work of \cite{sjodin_improving_1995, sjodin_convergence_1998} in Jaeckel's SDM design \cite{jaeckel1989class}, we show that as $n$ grows, autocorrelation tends to $0$.  But recall that as $n$ grows, the size of the critical distance also tends to $0$.  It is therefore crucial to select a value for $n$ in which the model will retain its convergence properties, with the understanding of the possible effects brought about by autocorrelation.   Systemwide properties such as these affect the entire behavior of the model and, as such, should always be taken into account by theoreticians and modelers alike.

@@

  \caption{Bongard problems 71 - 74, courtesy of Dr. Harry Foundalis\cite{foundalis_phaeaco:_2006, douglas1980godel, bongard_recognition_1968, Linhares2000}.  What distinguishes the boxes on the left hand side to those on the right hand side?  This is the quintessential `system-2' type of problem that current lies beyond AI's capabilities. The reader should note that here, for each class, $n=6$: a hard task for Machine Learning.}

@@

of the immense power of Artificial Intelligence.
